Sulfur Dioxide at Water's Surface

### 2010-12-20 Methods.tex
new image size for startingconfigurations, and reworded the text for the MD methods.

All simulations began with an equilibrated cube of 900 \wat~molecules, with sides of length 30\angs. The simulations all employed periodic boundaries to create an ``infinite-slab'' geometry for the water phase. One set of simulations involved adding a single \suldiox~to the center of the water box and then allowing the system to equilibrate over 1 ns of simulation. The system was then evolved for a further 2.5 ns with atomic coordinates written every 100 fs. The simulation is herein referred to as the ``surface equilibrated'' simulations.

\subsection{Steered Molecular Dynamics}

A second set of simulations involved preparing an equilibrated water slab as in the surface equilibrated method. A single \suldiox~was then introduced 20\angs above the slab, with the sulfur atom tethered to its initial position. The system was evolved for 1 ns, taking coordinate snapshots every 20 ps to create 50 starting points for further simulations. Steered molecular dynamics (SMD) were then performed to guide the \suldiox~down towards a tethered water 15\angs under the water slab surface by applying a small steering force.\cite{Isralewitz2001} The \suldiox~thus passed through the continuum of environments from gas phase to hydrate complex interaction, water surface adsorption, and absorption into the bulk of the neat-\wat~slab.

The third set of simulations were performed similarly to the neat-\wat~and single \suldiox~SMD simulations, but the water slab and gas phase above it were first saturated with \suldiox. The water slab was loaded internally with 22 \suldiox molecules, which represent a saturation level coinciding with the Henry's law constant for \suldiox~in \wat. The gas phase was populated with 50 \suldiox~molecules representing approx. 50 atm of \suldiox~pressure. As in the neat-\wat~SMD simulations, a single \suldiox~was introduced 20\angs above the saturated water slab surface and then steered into the bulk of the water. Figure \ref{fig:starting-configurations} illustrates two sample starting configurations for the SMD simulations, showing both the neat-\wat~slab and the saturated-\wat~slab configurations before steering the \suldiox~into the water bulk.

>>>>

All simulations began with an equilibrated cube of 900 \wat~molecules, with sides of length 30\angs. The long axis of each simulation cell (the axis normal to the water surface) was set to 120\angs. The simulations all employed periodic boundaries to create an ``infinite-slab'' geometry. After equilibrating the neat-\wat~slabs for 1 ns, two types of systems were created by introducing \suldiox.

One system involved the addition of a single \suldiox~molecule either within the bulk of the water slab, or above the slab surface. The single-\suldiox~system was then evolved for 2 ns to produce an equilibrated starting configuration. The second system introduced 22 \suldiox~molecules into the water slab in order to saturate it to a level coinciding with the Henry's law constant for \suldiox~in water. Additionally, 50 \suldiox~molecules were introduced into the gas phase outside of the water slab to simulate an added 50 atm of \suldiox~gas pressure. The saturated system was then evolved for 2 ns to produce a starting configuration for further simulations.

\subsection{Equilibrium Simulations}

Equilibrium simulations involved adding \suldiox~to a water slab and equilibrating as outlined above. One system had a single \suldiox~added to the center of the water box, representing a concentration of 0.06 M. The complementary high-concentration system with 22 \suldiox~molecule in the bulk represents a system of concentration 1.35 M, with an additional 50 \suldiox~in the gas phase to model 50 atm of pressure above the water surface. Both the low and high concentration systems were then evolved for a further 2.5 ns with atomic coordinates written every 100 fs.

\subsection{Steered Molecular Dynamics Simulations}

% need to add in the specifics about the SMD routine, force constants, calculations, etc.
A second set of simulations involved preparing an equilibrated water slab as in the surface equilibrated method above. However, for both the low and high concentration systems, a single \suldiox~was introduced 20\angs above the slab, with the sulfur atom tethered to its initial position. The system was evolved for 1 ns, taking coordinate snapshots every 20 ps to create 50 starting points for further simulations. Steered molecular dynamics (SMD) were then performed on the 50 system configurations (in both the low and high concentrations) to guide the \suldiox~down towards a tethered water 15\angs under the water slab surface by applying a small steering force.\cite{Isralewitz2001} The \suldiox~thus passed through the continuum of environments from gas phase to hydrate complex formation or interaction with surface-bound \suldiox, water surface adsorption, and absorption into the bulk of the \wat~slab.

Figure \ref{fig:starting-configurations} illustrates two sample starting configurations for the SMD simulations, showing both the neat-\wat~slab and the saturated-\wat~slab configurations before steering the \suldiox~into the water bulk.
